---
title: "How to use the GoogleImage2Array functions"
author: 
- name: Satoshi Kume
  email: satoshi.kume.1984@gmail.com
date: "`r Sys.Date()`"
graphics: no
package: GoogleImage2Array
output:
    BiocStyle::html_document:
        toc_float: false
vignette: >
    %\VignetteIndexEntry{How to use GoogleImage2array}
    %\VignetteIndexEntry{GoogleImage2Array}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("HowToUse.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Load packages

```{r echo=TRUE, eval=TRUE}
library(GoogleImage2Array)
```

# Get images via Google Image Search

`GoogleImage2array` function provide a 4-dimensional array of images via google image search.

```{r echo=TRUE, eval=TRUE}
#Search by persian cat
query <- "persian cat"
CatImg <- GoogleImage2array(query)

#show info
str(CatImg)
```

Multi-byte characters (e.g. Japanese) can also be used.

```{r echo=TRUE, eval=TRUE}
#Search by ペルシャ猫
query <- "ペルシャ猫"
CatImgJpn <- GoogleImage2array(query)

#show info
str(CatImgJpn)
```

# Display images with display.array

`display.array` show a result as a tiled image.

```{r echo=TRUE, eval=TRUE}
#display CatImg
display.array(CatImg)
```

# Get and Display images (`Display = TRUE` option)

The images are displayed in tiles by the option of GoogleImage2array function.

```{r echo=TRUE, eval=TRUE}
#Search by Shiba inu
query <- "Shiba inu"
DogImg <- GoogleImage2array(query, Display = TRUE)

#show info
str(DogImg)
```

# Combine two arrays together

```{r echo=TRUE, eval=TRUE}
#Bind two arrays to one array
ImgDat <- bind.array(CatImg, DogImg)

#show info
str(ImgDat)
```

# display images as a spiral image

```{r echo=TRUE, eval=FALSE}
#show images
display.spiral(CatImg)
```

```{r Fig001, fig.cap = "display images as a spiral image", echo = FALSE, out.width="75%"}
library(EBImage)
options(EBImage.display = "raster")
img <- system.file("images", "spiral.png", package="GoogleImage2Array")
EBImage::display(EBImage::readImage(files = img))
```

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
